Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate

### 2015-07-30 masters_paper/paper.tex
Penultimate for sections 1-3

    The second step is to fit a series of LASSO models of $\mathbf y$ on the combined design matrix $X_L:=[X \; \tilde X]$ so as to determine the largest value $\lambda$ at which the coefficient for each of $X_j$ and $\tilde X_j$ is nonzero.\footnote{Other statistics besides the $\lambda$s can also be used in the knockoff method, but are not considered in this paper} The subscript $L$ refers to the large design matrix with both features and knockoffs. Recall, for a given $\lambda$, the estimated coefficient from the LASSO regression will be 
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{\frac{1}{2}\|\mathbf y - X_L\mathbf b\|^2_2 + \lambda\|\mathbf{b}\|_1 \right\}\]
    In the general case, the ``LASSO path" refers to the path of solutions as $\lambda$ is decreased from $\infty$ to $0$, and we say that a features ``enters the path" at $\lambda$ when its coefficient is first estimated to be nonzero. One feature entering the LASSO path before another is an indication that the first feature is a stronger predictor of the outcome than the second. Thus, since, by construction, the knockoff features are weaker predictors than the originals, we would expect the original features to enter the LASSO path sooner than the knockoff features when the original is a valid predictor. On the other hand, since $\beta(\lambda)$ only depends on $X_L$ through the sufficient statistics $G_L:=X_L^TX_L$ and $X_L^T\mathbf y$, for null predictors, the coefficients of the original features won't enter any sooner on average than knockoff feature. This can be seen by switching a null $X_j$ with $\tilde X_j$; by construction, $G_L$ will be unaltered, while $\E\left[X_L^T\mathbf y\right]$ will also be unchanged, since $\E[X_j^T\mathbf y]=\E[\tilde X_j^T\mathbf y]=0$. \par
   This observation leads to the final step. Let $Z_j$ be the largest $\lambda$ such that feature $j$ has a nonzero coefficient and $\tilde Z_j$ the largest $\lambda$ such that knockoff $j$ has a nonzero coefficient. Then, define $W_j$ as 

@@

            When $X_j$ is a null predictor, $W_j$ will be symmetrically distributed around zero, and when $X_j$ is true predictor, it will have a distribution skewed positive. Since $W_j$ with large positive values are more likely to be true predictors, the knockoff filter selects the variables $\{j:W_j\geq T\}$, where $T$ is a threshold defined as

@@

            Basic logic of this method is fairly simple. Let $N_h(t)$ be the random variable for the number of null predictors with $W_j\leq t$, $N_l(t)$ be the number of null predictors with $W_j\geq t$, and $V_l(t)$ \& $V_h(t)$ be the similar number of true predictors. Since the null $W_j$ are symmetrically distributed around $0$, $\E[N_l(t)]=\E[N_h(t)]$. Thus,
                q &\geq \E\left[ \frac{\vert\{j:W_j\leq -t\}\vert}{\max\{\vert\{j:W_j\geq t\}\vert,1\}} \right] \\
                q &\geq \E\left[ \frac{N_l(t) + V_l(t)}{\max\{N_h(t) + V_h(t),1\}} \right] \\
                q &\geq \E\left[ \frac{N_l(t)}{\max\{N_h(t) + V_h(t),1\}} \right] \\
                q &\geq \E\left[ \frac{N_h(t)}{\max\{N_h(t) + V_h(t),1\}} \right] \\
                q &\geq \textrm{FDR}
            So FDR is controlled, and since $V_l(t)$ will tend to be small, it should be controlled fairly tightly.

\subsection{Original Knockoff Features}
    The original formulation of the method offers two similar methods of constructing knockoffs. Both of these will, by construction, have exactly the property that
    \[ \tilde X^T\tilde X=G \textrm{ and } \tilde X^T X = G - \diag{\mathbf s}.\]
    For both methods, the first step is to normalize the matrix $X$ such that $X_j^TX_j=1$ for all $j$. Then, let the Gram matrix of $X_L$ is
    \[ G_L= [X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right] \]
    $A$, the Schur complement of $G$ in $G_L$ can be calculated as 
    \[ A = 2\,\diag{\mathbf s} - \diag{\mathbf s}G^{-1}\diag{\mathbf s} \]
    For $G_L$ to exist, $G_L$ must be positive semi-definite, which happens if and only if $A$ is positive semi-definite, which happens in turn if and only if\footnote{A fleshed out version of this argument can be found in the original knockoff paper} 
    \[ \diag{\mathbf s} \succeq 0  \; \textrm{ and } \; 2G - \diag{\mathbf s} \succeq 0 \]
    Given this is true, $A$ can be factored as $A=C^TC$. Combining this with a satisfactory $\mathbf s$ and an orthonormal matrix $\tilde U\in\R^{n\times p}$ such that $\tilde U^T X = 0$, a $\tilde X$ fulfilling the desired properties can be calculated as 
    \[ \tilde X = X(I-G^{-1}\,\diag{\mathbf s}) + \tilde UC\]
    As mentioned above, $\mathbf s$ should be chosen so as to make $\diag{G}-\mathbf s$ small. Since each $X_j$ has been normalized, this means that $\diag{G}=\mathbf 1$, so $\mathbf 1 - \mathbf s$ should be minimized in accordance with the restrictions on $\mathbf s$. The two methods differ in how $\mathbf s$ is chosen:
    \begin{itemize}
        \item \textit{Equi-correlated knockoffs}: Each original features is set to have the same correlation with its knockoff by setting $\mathbf s = 2\min\{\lambda_{min}(G),1\}\mathbf 1$. For all simulations in this paper, this was the method used.
        \item \textit{SDP knockoffs}: The $\mathbf s$ which minimizes the average correlation between knockoff and original features can be found via a semi-definite programing problem:
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf1-\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2G $
                \end{tabular} 
            \end{center}
            This method is significantly more computationally intensive. 
    \end{itemize}

\subsection{Binary Knockoffs}
    Though the ``original" knockoff method, described above, achieves the exact desired knockoff properties, the individual values in the vector $X_j$ will have little relation to the individual values in $X_j$. In particular, these values will often have very different empirical distributions. This effect is particularly noticeable when the random variable $x_j$ is discrete but $\tilde X_j$ does not even consist of the same set of values. The end result is that for variable selection for other generalized linear models, which do not have the same sufficient statistics as linear regression which knockoffs are designed to hit, the original knockoffs will fail to control FDR. \par
    Thus, this paper offers a new method of generating knockoffs which should offer superior performance with other GLMs. In this new method, the matrix of knockoff features $\tilde X$ will be generated by row from a random vector valued variable $\mathbf{\tilde x}$, each entry $\tilde x_j$ of which will have the property $\tilde x_j \sim x_j$. This random variable will also abide by a relaxation of the original knockoff condition:
    \[ \E[\mathbf{\tilde x}^T\mathbf{\tilde x}]=G \; \textrm{ and } \; \E[\mathbf{\tilde x}^T \mathbf x \st \mathbf x] = G - \diag{\mathbf s}\]
    This will ensure that, at the very least, these knockoffs are a suitable replacement for the original knockoffs for linear regression. \par
    Generating such knockoffs for a completely general case of any $\mathbf x$ is likely infeasible. However, in the specific case where $\mathbf x$ is a random binary vector variable, this paper will demonstrate a method to generate such knockoff variables. Since binary data is extremely common in many areas, this will hopefully serve as a useful tool.

\subsection{Paper Organization}
The rest of this paper will be organized in the following fashion:
\begin{itemize}
    \item Section 2 will go into more detail about how the original knockoffs breakdown with generalized linear models. In particular, several simulations will demonstrate how they breakdown.
    \item Section 3 will develop the method and theory for generating binary knockoffs.
    \item Section 4 will discuss tests of Binary knockoffs in simulation, both in comparison to the original knockoffs with LASSO and for logistic regression by itself.
    \item Section 5 is the final section, and will contain discussion of the results as well as areas for further work.
\end{itemize}

\section{Issues With Deterministic Knockoffs} 
    The knockoff filter and $W$ statistics have a very natural extension to generalized linear models. Here, where $l(\beta\st X, \tilde X)$ is the log likelihood of coefficients $\beta$ given the model, the $L1$ regularized regression model will have estimated coefficient vector
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{l(\beta\st X, \tilde X) + \lambda\|b\|_1 \right\}\]
    The $Z_j$ and $\tilde Z_j$ are then, once again, the largest $\lambda$ such that the given original or knockoff feature has a positive coefficient, and then $W_j$ is constructed exactly as before. The problem with this is that if the given GLM doesn't have the same sufficient statistics as linear regression, there is no theoretical guarantee that the knockoff filter will control FDR. This is since, for null $X_j$, there is no theory to guarantee the $Z_j$ and $\tilde Z_j$ are exchangeable, and thus $W_j$ is not guaranteed to be symmetrically distributed around $0$. \par
    \begin{figure}[h]
        \begin{center}
        \includegraphics[width=14cm]{images/entryrate_original_logit}
    \end{center}
        \caption{The mean cumulative portion of $W$ statistic which are positive by absolute rank of the value. The mean is over 1000 simulations. On the left side, the features are drawn from a random standard normal distribution. On the right side, they are drawn as Bernoulli with probability $.25$ of being 1. The top has 50 null features, while the bottom has 40 null features with the outcome and 10 correlated with it.}
    \end{figure}

    To test how bad this problem is, I tested the method using original style knockoffs in logistic regression. The results can be seen in figure 1, which shows cumulatively, starting with the largest absolute value, what portion of the $W_j$ are positive. For the method to work, for the null predictors, this should be a consistent $50\%$, indicative of the desired symmetric distribution. This is particularly important for high values, which play the largest roll in selecting a threshold. We see that in the top left corner, when all features are null and normally distributed, that we almost achieve this, with only a small, but consistent, deviation from $50\%$. However, in the top right, when the predictors are binary, the null originals enter first far more often, which will result in the FDR being too high. \par
    \FloatBarrier
    This gets much worse when some true predictors are included, as shown in the bottom row of the figure. For both normal and binary predictors, the originals come in first far more often in the beginning. This will completely ruin FDR control, since the portion of null predictors will be assumed far lower than it actually is. It is worth noting that the particular shape of the curve in the diagram, with the plateau for the null predictors through 10, is partially an artifact of how the totals were tabulated. The mean through the first ten is the mean for null predictors that came in first out of both null and true predictors; since the largest ten $W_j$ will tend to be true predictors, the average over the null predictors represent the few extreme $W_j$ which managed to beat out some number of true predictors.  \par
    \begin{figure}[h]
        \includegraphics[width=14cm]{images/normalQQ}
        \caption{Normal Q-Q of original variables and knockoffs for simulation with $4$ variables and 1,000 observations}
    \end{figure}

    Upon examination, the issue seems to be that the original style knockoff features have a very different empirical distribution than the features they are imitating. This is obviously true with the binary features, but even with the normal features, the distributions differ a lot. In figure 2, the distribution of four feature and the original style knockoff are plotted against a normal distribution in Q-Q plots. As you can see, they don't match at all. This is suggestive of a solution; if the knockoff variables match the marginal distribution of the original features better, the result may be more suitable for FDR control in GLMs. \par
    \FloatBarrier

\section{Random Binary Knockoffs}
Random binary knockoffs $\mathbf{\tilde x}$, which maintain the correlation condition in expectation, fit the bill in this regard. The method to produce them is based heavily on more general methodology to random binary vector variables with internal correlation.

\subsection{Random Binary Vector Generation}
The full class of random binary vector variables on $\{0,1\}^p$ can be specified as multinomial on the $2^p$ elements of the set. However, in practice, it is generally impractical to specify or estimate all $2^p$ necessary parameters, so it is useful to, as is desirable for knockoffs, pick a method to match the first two moments. These are the mean vector $\E(\bf x)=m\in(0,1)^p$ and the cross-moment matrix $\E(\bf x\bf x^T)=M\in(0,1)^{p\times p}$. Obviously, $m_i = \p(x_i=1)$, $M_{ij} = \p(x_i=x_j=1)$, and $\mathbf m=\diag{M}$. For an arbitrary symmetric $M$ to be valid cross-moment matrix for some random binary vector variable, $M-mm^T\succeq0$, and
    \[ \max\{0,m_i+m_j -1\} \leq M_{ij} \leq \min\{m_i,m_j\}\]
    for all $i\neq j.$ Given a qualifying $M$, or observed $X$, there are then a few methods for generating additional random values.

\subsubsection{Gaussian Copula Family}
Since multivariate normal distributions are easy to randomly draw from and defined by their first two moments, an obvious choice is to use them to generate random binary vectors. This might be done by finding $\mu$ and $\Sigma$ such that for $\mathbf z\sim N_p(\mu,\Sigma)$, $x_i$ can be generated as $x_i = \mathrm{sign}(z_i)$, and have the desired first two moments. However, this is only guaranteed to be feasible in the bivariate case. For higher dimensions, this method can generally only provide random binary vectors with approximately the right moments, and the quality of the approximation quickly degenerates as $p$ increases.

\subsubsection{$\mu$-Conditionals family}
    There exists a more flexible family which will always work for arbitrary $M$ called $\mu$-conditionals. The basic idea is that the $X$ is generate sequentially as 
    \[ \p(x_{i}=1\st x_{1},...,x_{i-1}) = \mu\left(a_{ii}+\sum_{k=1}^{i-1}a_{ik}x_i\right) \]
    for some monotone function $\mu:\R\to(0,1)$. This is essentially a binomial family GLM for a link function $\mu$. If one takes all of the $a_{kj}$, they can form a lower triangular matrix $A$, and then the joint density can be expressed as

    \[ \p(\mathbf x=\mathbf \gamma) \propto \mu(\mathbf{\gamma}^T A\mathbf \gamma)\]

>>>>

    The second step is to fit a series of LASSO models of $\mathbf y$ on the combined design matrix $X_{aug}:=[X \; \tilde X]$ so as to determine the largest value $\lambda$ at which the coefficient for each of $X_j$ and $\tilde X_j$ is nonzero.\footnote{Other statistics besides the $\lambda$s can also be used in the knockoff method, but are not considered in this paper} The subscript $aug$ refers to the augmented design matrix with both features and knockoffs. Recall, for a given $\lambda$, the estimated coefficient from the LASSO regression will be 
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{\frac{1}{2}\|\mathbf y - X_{aug}\mathbf b\|^2_2 + \lambda\|\mathbf{b}\|_1 \right\}\]
    In the general case, the ``LASSO path" refers to the path of solutions as $\lambda$ is decreased from $\infty$ to $0$, and we say that a features ``enters the path" at $\lambda$ when its coefficient is first estimated to be nonzero. One feature entering the LASSO path before another is an indication that the first feature is a stronger predictor of the outcome than the second. Thus, since, by construction, the knockoff features are weaker predictors than the originals, we would expect the original features to enter the LASSO path sooner than the knockoff features when the original is a valid predictor. On the other hand, since $\beta(\lambda)$ only depends on $X_{aug}$ through the sufficient statistics $G_{aug}:=X_{aug}^TX_{aug}$ and $X_{aug}^T\mathbf y$, for null predictors, the coefficients of the original features won't enter any sooner on average than knockoff feature. This can be seen by switching a null $X_j$ with $\tilde X_j$; by construction, $G_{aug}$ will be unaltered, while $\E\left[X_{aug}^T\mathbf y\right]$ will also be unchanged, since $\E[X_j^T\mathbf y]=\E[\tilde X_j^T\mathbf y]=0$. \par
   This observation leads to the final step. Let $Z_j$ be the point at which $X_j$ entered the path and $\tilde Z_j$ the point at which $\tilde X_j$ entered the path. Then, define $W_j$ as 

@@

            $W_j$ is positive when $Z_j$ entered the path first and negative when $\tilde X_j$ entered the path first. Large, positive values for $W_j$ will indicate that $X_j$ is a strong predictor, since $X_j$ entered the path early and before $\tilde X_j$. Thus, we will make a selection $\hat S=\{j:W_j\geq T\}$ for some threshold $T$. When $X_j\not\in S$, $X_j$ and $\tilde X_j$ are both equally likely to enter the path first, so $W_j$ is equally as likely to be positive as negative for $j\in S$. Thus, 
            \[ \vert\{j:W_j\geq T \; \& \; j\not\in S\}\vert \approx \vert\{j:W_j\leq -T \; \& \; j\not\in S\}\vert] \]
            The quantity on the left is, of course, the number of false discoveries made by choosing a particular threshold $T$. Also, it must be the case
            \[\vert \{j:W_j\leq -T \; \& \; j\not\in S\}\vert \leq \vert\{j:W_j\leq -T\}\vert\]
            This inequality should be pretty tight, since a true predictor should be a better predictor than its knockoff and unlikely to enter the path after it. Accordingly, the expected portion of false discoveries out of all discoveries is approximately
            \[FDR \approx \E\left[\frac{\vert\{j:W_j\leq -T\}\vert}{\max\{\vert\{j:W_j\geq T\}\vert,1\}}\right]\] 
            So, when $T$ is selected as

@@

            FDR should be controlled at level $q$.

\subsection{Original Knockoff Features}
    The original formulation of the method offers two similar methods of constructing knockoffs. Both of these will, by construction, have exactly the property that
    \[ \tilde X^T\tilde X=G \textrm{ and } \tilde X^T X = G - \diag{\mathbf s}.\]
    For both methods, the first step is to normalize the matrix $X$ such that $X_j^TX_j=1$ for all $j$. The Gram matrix of $X_{aug}$ is
    \[ G_{aug}= [X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right] \]
    $A$, the Schur complement of $G$ in $G_{aug}$ can be calculated as 
    \[ A = 2\,\diag{\mathbf s} - \diag{\mathbf s}G^{-1}\diag{\mathbf s} \]
    For $G_{aug}$ to exist, $G_{aug}$ must be positive semi-definite, which happens if and only if $A$ is positive semi-definite, which happens in turn if and only if 
    \[ \diag{\mathbf s} \succeq 0  \; \textrm{ and } \; 2G - \diag{\mathbf s} \succeq 0 \]
    Given this is true, $A$ can be factored as $A=C^TC$. Combining this with a satisfactory $\mathbf s$ and an orthonormal matrix $\tilde U\in\R^{n\times p}$ such that $\tilde U^T X = 0$, a $\tilde X$ fulfilling the desired properties can be calculated as 
    \[ \tilde X = X(I-G^{-1}\,\diag{\mathbf s}) + \tilde UC\]
    As mentioned above, $\mathbf s$ should be chosen so as to make $\diag{G}-\mathbf s$ small. Since each $X_j$ has been normalized, this means that $\diag{G}=\mathbf 1$, so $\mathbf 1 - \mathbf s$ should be minimized in accordance with the restrictions on $\mathbf s$. The two methods differ in how $\mathbf s$ is chosen:
    \begin{itemize}
        \item \textit{Equi-correlated knockoffs}: Each original features is set to have the same correlation with its knockoff by setting $\mathbf s = 2\min\{\lambda_{min}(G),1\}\mathbf 1$. For all simulations in this paper, this was the method used.
        \item \textit{SDP knockoffs}: The $\mathbf s$ which minimizes the average correlation between knockoff and original features can be found via a semi-definite programing problem:
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf1-\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2G $
                \end{tabular} 
            \end{center}
            This method is significantly more computationally intensive. 
    \end{itemize}

\subsection{Binary Knockoffs}
    Though the ``original" knockoff method, described above, achieves the exact desired correlation properties, the individual values in the vector $X_j$ will have little relation to the individual values in $X_j$. In particular, these values will often have very different empirical distributions. This effect is particularly noticeable when the random variable $x_j$ is discrete but $\tilde X_j$ does not even consist of the same set of values. The end result is that for variable selection for other generalized linear models, which do not have the same sufficient statistics as linear regression which knockoffs are designed to hit, the original knockoffs will fail to control FDR. \par
    Thus, this paper offers a new method of generating knockoffs for binary data which should offer superior performance with other GLMs. In this new method, the matrix of knockoff features $\tilde X$ will also be binary, generated randomly so as to hit the new correlation condition
    \[ \E[\mathbf{\tilde x}^T\mathbf{\tilde x}]=\Sigma \; \textrm{ and } \; \E[\mathbf{\tilde x}^T \mathbf x \st \mathbf x] = \Sigma - \diag{\mathbf s}\]
    Where $\Sigma$ is the covariance matrix of $X$. This is essentially relaxation of the original correlation condition, requiring the desired covariance to only hold in expectation. For large values of $n$, the observed covariance will converge to its expectation, making this distinction minor.

\subsection{Paper Organization}
The rest of this paper will be organized in the following fashion:
\begin{itemize}
    \item Section 2 will go into more detail about how the original knockoffs break down with generalized linear models. In particular, several simulations will demonstrate how they fail to control FDR.
    \item Section 3 will develop the method for generating binary knockoffs.
    \item Section 4 will discuss tests of binary knockoffs in simulation, comparing their performance to the original knockoffs for both linear and logistic regression. 
    \item Section 5 is the final section, and will contain discussion of the results as well as areas for further work.
\end{itemize}

\section{Issues With Deterministic Knockoffs} 
    The knockoff filter and $W$ statistics have a very natural extension to generalized linear models. Here, where $l(\beta\st X, \tilde X)$ is the log likelihood of coefficients $\beta$ given the model, the $L1$ regularized regression model will have estimated coefficient vector
    \[ \beta(\lambda) = \argmin_\mathbf b \left\{l(\mathbf{b}\st X, \tilde X) + \lambda\|\mathbf{b}\|_1 \right\}\]
    The $Z_j$ and $\tilde Z_j$ are then, once again, the largest $\lambda$ such that the given original or knockoff feature has a positive coefficient, and then $W_j$ is constructed exactly as before. The problem with this is that if the given GLM doesn't have the same sufficient statistics as linear regression, there is no theoretical guarantee that the knockoff filter will control FDR. This is since, for null $X_j$, there is no theory to guarantee the $Z_j$ and $\tilde Z_j$ are exchangeable, and thus $W_j$ is not guaranteed to be symmetrically distributed around $0$. \par
    \begin{figure}[h]
        \begin{center}
        \includegraphics[width=14cm]{images/entryrate_original_logit}
    \end{center}
        \caption{The mean cumulative portion of $W$ statistic which are positive by absolute rank of the value. The mean is over 1000 simulations. On the left side, the features are drawn from a random standard normal distribution. On the right side, they are drawn as Bernoulli with probability $.25$ of being 1. The top has 50 null features, while the bottom has 10 features in the true model, and 40 null features.}
    \end{figure}

    To evaluate whether this made a difference in practice, I tested the method using original style knockoffs in logistic regression. The results can be seen in figure 1, which shows cumulatively, starting with the largest absolute value, what portion of the $W_j$ are positive. For the method to work, for the null predictors, this should be a consistent $50\%$, indicative of the desired symmetric distribution. This is particularly important for high values, which play the largest roll in selecting a threshold. In the top left corner, under the ``global null", where all features are null and normally distributed, that we almost achieve this. There is just a small, but consistent, deviation from $50\%$. However, in the top right, when the predictors are binary but still all null, the originals enter first far more often, which will result in the FDR being too high. \par
    \FloatBarrier
    This gets much worse when some true predictors are included, as shown in the bottom row of the figure. For both normal and binary predictors, the originals come in first far more often in the beginning. This will completely ruin FDR control, since the portion of null predictors will be assumed far lower than it actually is. It is worth noting that the particular shape of the curve in the diagram, with the plateau for the null predictors through 10, is partially an artifact of there being 10 true signals. The mean through the first ten is the mean for null predictors that came in first out of both null and true predictors; since the largest ten $W_j$ will tend to be true predictors, the average over the null predictors represent the few extreme $W_j$ which managed to beat out some number of true predictors.  \par
    \begin{figure}[h]
        \begin{center}
            \includegraphics[width=14cm]{images/normalQQ}
            \caption{Normal Q-Q of original variables and knockoffs for simulation with $4$ variables and 1,000 observations}
        \end{center}
    \end{figure}
    Upon examination, the issue seems to be that the original style knockoff features have a very different empirical distribution than the features they are imitating. This is obviously true with the binary features, but even with the normal features, the distributions differ substantially. In figure 2, the distribution of four features and their original style knockoff are plotted against a normal distribution in Q-Q plots. As you can see, the distributions differ substantially. This is suggestive of a solution; if the knockoff variables match the marginal distribution of the original features better, the result may be more suitable for FDR control in GLMs. \par
    \FloatBarrier

\section{Random Binary Knockoffs}
Coming up with knockoffs which would match the original features' marginal distributions better for arbitrary $X$ is daunting problem. Limiting ourselves to binary data, which is common in real world applications, presents a far more manageable case. However, solving for a binary $\tilde X$ which matches the correlation condition exactly or closely is an integer programing problem, which are generally NP-hard. Thus, instead, this section will develop methods of generating $\tilde X$ randomly such that the correlation condition holds in expectation. Mainly, $\tilde X\st X$ should be a random matrix such that
        \[ \E(X^T \tilde X \st X) = X^TX - \diag{s} \quad \& \quad \E(\tilde X^T \tilde X \st X) = X^TX\]

\subsection{Random Binary Vector Variables}
We can imagine each row of $X$ being an observation of a random binary vector variable $\mathbf x$. The full class of random binary vector variables on $\{0,1\}^p$ can be specified as multinomial on the $2^p$ elements of the set. However, in practice, it is generally impractical to specify or estimate all $2^p-1$ necessary parameters, so it is useful to pick a method to match the first two moments, as is desirable for knockoffs. These are the mean vector $\E(\bf x)=m\in[0,1]^p$ and the cross-moment matrix $\E(\bf x\bf x^T)=M\in[0,1]^{p\times p}$. Obviously, $m_i = \p(x_i=1)$, $M_{ij} = \p(x_i=x_j=1)$, and $\mathbf m=\diag{M}$. For an arbitrary symmetric $M$ to be a valid cross-moment matrix for some random binary vector variable, $M-mm^T\succeq0$, and
    \[ \max\{0,m_i+m_j -1\} \leq M_{ij} \leq \min\{m_i,m_j\}\]
    for all $i\neq j$\cite{2011arXiv1111.0576S}.

\subsection{Relaxed Correlation Condition}
As before with the original knockoffs, the first step of generating knockoffs is to decide on the target correlation structure for $X_{aug}$. For binary knockoffs, this is done by selecting the target covariance matrix $\Sigma_{aug}$. This is extremely similar, though not identical, to the method with the original knockoffs, where $X_{aug}^TX_{aug}$ after normalization was targeted. However, much the same method as before can be used. Let the vector of empirical means of the columns of $X$ be $\mathbf m = \frac{1}{n}X^T\mathbf 1$ and the empirical covariance matrix of $X$ be $\Sigma = \frac{1}{n}X^TX - \mathbf{m}\mathbf{m}^T$. Much as before with the original knockoffs, both the equi-correlated and SDP method can be used to select  $\mathbf s$  such that $\diag{\Sigma}-\mathbf s$ is small and 
        \[ \Sigma_{aug} = \left[\begin{array}{cc}  \Sigma & \Sigma - \diag{\mathbf s }\\ \Sigma - \diag{\mathbf s} & \Sigma \end{array}\right] \succeq 0 \]
    While with the original knockoffs, the result was small values for $X_i^T\tilde X_i$, now the result is low covariance between $X_i$ and $\tilde X_i$.\par
    Additionally though, the moment condition must hold for $\Sigma_{aug}$ to correspond to a proper random binary vector. If 
    \[\mathbf m_{aug} = \E\left(\mathbf x_{aug}\right) = \left[\begin{array}{c}\mathbf m \\ \mathbf m \end{array}\right] \]
    then the desired cross-moment matrix of the joint distribution is 
        \[ M_{aug} = \Sigma_{aug} + \mathbf m_{aug}\mathbf m_{aug}^T\]
        So it must be the case that  
        \[\max\{0,\mathbf m_{aug,i} + \mathbf m_{aug,j} -1\} \leq \Sigma_{aug,ij} + \mathbf m_i \mathbf m_j \leq \min\{\mathbf m_{aug,i}, \mathbf m_{aug,j}\} \]
        However, since $\Sigma$ and $\mathbf m$ are from an actual random binary vector, the entries of $\Sigma$ satisfy this property by default. Only off diagonal entries which have had $\mathbf s$ subtracted from them could possibly violate this condition. Furthermore, for these entries, the goal is to make $\Sigma_{aug,ij}$ as close to $0$ as possible. Since the condition is always satisfied in a neighborhood of $M_{aug,ij} = m_{aug,j}m_{aug,i}$, this implies that this method should normally be satisfied. This is the principle advantage minimizing the $\textrm{cor}(x_i,\tilde x_i)$ rather than $\E[x_i\tilde x_i]$. For the SDP method though, the restriction can be built directly into the optimization problem. If $\sigma = \diag{\Sigma}^{\frac{1}{2}}$ is the vector of standard deviations, the updated problem is
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf 1-\diag{\sigma}^{-1}\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2\Sigma $ \\
                               & $ \max(2m_i -1,0) \leq \Sigma_{ii}-\mathbf s_i + m_i^2 \leq m_i  \quad \forall i$
                \end{tabular} 
            \end{center} 
            the factor of $\diag{\sigma}^{-1}$ in the objective is to account for the $x_i$ not being normalized, as was the case with the original knockoffs. \par
            Given the $\sigma_{aug}$ and corresponding $M_{aug}$, all that is needed is some process to generate $\tilde X$ that replicates the desired empirical cross moments.

\subsection{Fitting via Quadratic Programing}
        The simplest way to do this is based on a probability matrix $P\in (0,1)^{n\times p}$, where each $X_{ij}$ is drawn independently as $X_{ij}\sim\textrm{Bernoulli}(P_{ij})$. Such a $P$, to give as close as possible to the desired cross-moments, should satisfy 
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|X^TP-(M-\diag{s})\|_{fro}^2 + \sum_{i\neq j}(P_i^T P_j - M_{ij})^2 $\\
                    subject to   & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
            The first part of the objective corresponds to the deviation of $\E[X^T\tilde X]$ from $M-\diag{s}$ and the second part to the deviation of $\E[\tilde X^T \tilde X]$ from $M$, excluding the diagonal values which are matched by $ \mathbf 1^T P = \mathbf m $. This problem can be stated as a quadratic program via the introduction of slack variables:
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|W\|_{fro}^2 + \|V\|_{fro}^2 $ \\
                    subject to   & $ -W \leq X^TP-(M-\diag{s})\leq W $ \\
                                 & $ -V_{ij} \leq P_i^T P_j - M_{ij} \leq V_{ij} \quad \forall i\neq j$ \\
                                 & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}

            Though there are powerful tools and theory for solving quadratic programs, $n\times p$ would have to be fairly small for this optimization problem to be computationally reasonable in practice. Ideally, there would be a method to split up this problem into a series of smaller optimization problems which would yield the same solution. An optimist might hope that iterating through the columns of $P$, optimizing each to hit its desired cross-moments individually conditioned on the estimate of the rest of $P$, would achieve this. In practice, this does seem to yield reasonable results, and is far quicker than other methods for large $p$. In particular, the following method seemed to work well:
    \begin{enumerate}
        \item Optimize initial $P_i$ as such that $X_j^T P_i = M_{ij}$ if $i\neq j$ and $X_i^T P_i = \sigma_i(1-s)$.   
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $ \left(\frac{1}{n}X_i^T P_i - (M_{ij}-\sigma_i(1-s))\right)^2 + \sum_{i\neq j}(\frac{1}{n}X_j^T P_i - M_{ij})^2$ \\
                    subject to   & $ \frac{1}{n}\mathbf 1^T P_i = M_{ii} $ \\
                                 & $0 \leq P_i \leq 1$
                \end{tabular} 
            \end{center}
        \item Draw initial $\tilde X_i$ as independent Bernoulli with probability $P_i$.
        \item Iterate through $1\leq i \leq p$, fitting new $P_i$ such that 
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $ \left(\frac{1}{n}X_i^T P_i - (M_{ij}-\sigma_i(1-s))\right)^2 + \sum_{i\neq j}(\frac{1}{n}X_j^T P_i - M_{ij})^2 + \sum_{i\neq j}(\frac{1}{n}\tilde X_j^T P_i - M_{ij})^2$  \\
                    subject to   & $ \frac{1}{n}\mathbf 1^T P_i = M_{ii} $ \\
                                 & $0 \leq P_i \leq 1$
                \end{tabular} 
            \end{center}
            After each $P_i$ is fit, redraw $\tilde X_i$ as independent Bernoulli with probability $P_i$.
    \end{enumerate}
    Drawing the $\tilde X_i$ after each step, rather than just leaving the $P_i$, seems counter intuitive, but under experimentation, it seemed to provide better results. As well, though the third step may be repeated several times, in practice this didn't lead to improvement.

\subsection{Fitting via Conditional Random Binary Vectors }
An alternate approach to generating $\tilde X$ that will satisfy the relaxed correlation condition is to find a random binary vector $\mathbf{x}_{aug}\in\{0,1\}^{2p}$ that has the desired cross-moments $M_{aug}$. Let $\mathbf{x}_{aug,1}$ be the first $p$ entries of $\mathbf{x}_{aug}$ and $\mathbf{x}_{aug,2}$ be the remainder. Then, for a row $\xi$ of $X$, the corresponding row $\tilde \xi$ of $\tilde X$ would be drawn from $\mathbf{x}_{aug,2}\st \mathbf{x}_{aug,1}=\xi$. This necessitates a family of binary vectors which can match any cross-moment matrix and is easy to conditionally sample from.

\subsubsection{Gaussian Copula Family}
Since multivariate normal distributions are quite easy to sample from and are defined by their first two moments, an obvious choice is to use them to generate random binary vectors. This might be done by finding $\mu$ and $\Sigma$ such that for $\mathbf z\sim N_p(\mu,\Sigma)$, where $x_i$ is defined as $x_i = \mathrm{sign}(z_i)$, $\mathbf x$ has the desired first two moments. However, this is only guaranteed to be feasible in the bivariate case. For higher dimensions, this method can generally only provide random binary vectors with approximately the right moments, and the quality of the approximation quickly degenerates as $p$ increases\cite{2011arXiv1111.0576S}. Therefore, we do not explore this direction further.

\subsubsection{$\mu$-Conditionals family}
There exists a more flexible family which will always work for arbitrary $M$ called $\mu$-conditionals\cite{2011arXiv1111.0576S}. The basic idea is that the entries of a binary vector variable $\mathbf x$ can be sampled sequentially as 
    \[ \p(x_{i}=1\st x_{1},...,x_{i-1}) = \mu\left(a_{ii}+\sum_{k=1}^{i-1}a_{ik}x_i\right) \]
    for some monotone function $\mu:\R\to(0,1)$. This is essentially a binomial family GLM for a link function $\mu$. If one takes all of the $a_{kj}$, they can form a lower triangular matrix $A$, and then the joint density can be expressed as

    \[ \p(\mathbf x=\mathbf \xi) \propto \mu(\mathbf{\xi}^T A\mathbf \xi)\]
